Project Setup

### 2024-11-27 setup.qmd
Use APA citation style
Mention v2 of Data Package standard

---
title: "Project Setup"
lang: en
bibliography: literature.bib
engine: knitr
---

@@

Specifically, one can use the R package [`frictionless`](https://docs.ropensci.org/frictionless/) to create a _schema_ which describes the structure of the data. For the purpose of the following code, it is just a nested list that we edit to include our own information. We also explicitly record in the schema that missing values are stored in the data file as `NA` and that the data are licensed under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/). Finally, the package is used to create a metadata file that contains the schema.

>>>>

---
title: "Project Setup"
lang: en
engine: knitr
---

@@

Specifically, one can use the R package [`frictionless`](https://docs.ropensci.org/frictionless/) to create a _schema_ which describes the structure of the data.^[In June 2024, [version 2](https://datapackage.org/) of the frictionless data standard has been released. As of November 2024, the R package `frictionless` only supports the first version, though support for v2 is [planned](https://github.com/frictionlessdata/frictionless-r/labels/datapackage%3Av2).] For the purpose of the following code, it is just a nested list that we edit to include our own information. We also explicitly record in the schema that missing values are stored in the data file as `NA` and that the data are licensed under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/). Finally, the package is used to create a metadata file that contains the schema.
